Turbulence in compact to giant HII regions

### 2022-06-24 Corr.tex
Javier changes 2022-06-24

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
 log $\sigma$ &            log L(H) &    0.27 $\pm$ 0.1 &  -9.57 $\pm$ 3.95 &   0.86 &  0.003 \\
    log $r_0$ &             log $S$ &   0.94 $\pm$ 0.34 &  -1.67 $\pm$ 0.74 &   0.85 &  0.004 \\
 %log $\sigma$ &  log $\sigma_{LOS}$ &   0.75 $\pm$ 0.59 &  -0.15 $\pm$ 0.69 &   0.62 &   0.07 \\
 log $\sigma$ &         log $r_{0}$ &   0.17 $\pm$ 0.18 &   0.68 $\pm$ 0.13 &    0.5 &  0.168 \\
      log $m$ &            log Dist &   -0.06 $\pm$ 0.1 &    1.11 $\pm$ 0.2 &  -0.38 &   0.32 \\
      log $m$ &         log $r_{0}$ &  -0.03 $\pm$ 0.09 &    0.0 $\pm$ 0.06 &  -0.24 &  0.529 \\
      log $m$ &        log $\sigma$ &  -0.12 $\pm$ 0.31 &   0.08 $\pm$ 0.23 &  -0.24 &  0.536 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &       log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
 log $\sigma$ &      log L(H) &   0.26 $\pm$ 0.11 &  -9.19 $\pm$ 4.33 &   0.86 &  0.003 \\
 log $\sigma$ &       log $S$ &   0.24 $\pm$ 0.17 &   0.24 $\pm$ 0.38 &   0.64 &   0.06 \\
 log $\sigma$ &   log $r_{0}$ &   0.18 $\pm$ 0.17 &   0.69 $\pm$ 0.12 &   0.51 &  0.164 \\
      log $m$ &      log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
      log $m$ &  log $\sigma$ &  -0.18 $\pm$ 1.03 &   0.14 $\pm$ 0.74 &  -0.37 &  0.327 \\
      log $m$ &   log $r_{0}$ &  -0.02 $\pm$ 0.07 &   0.01 $\pm$ 0.05 &  -0.28 &  0.469 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

### 2022-06-24 strucfunc_paper.tex
Javier changes 2022-06-24

\subsection{Comparison with previous structure functions}
\label{sec:comp-with-prev}
Comparison with prior studies is complicated by the
diversity of methodologies that  have been employed.
There is almost universal agreement on how to measure
the velocity variance \(\sigma^2\pos\),
although even here there can be small differences according
to whether the centroid velocities come from gaussian fitting
or velocity moments,
and whether or not smooth large-scale trends are first removed.
\citet{arthur2016turbulence} compared multiple studies of the
inner Orion Nebula, finding agreement to within 20\%
in \(\sigma^2\pos\) determinations
for emission lines that trace the bulk of the fully ionized gas.

@@

\section{\boldmath Notes on individual \hii{} regions}
\label{sec:notes-individual-hii}
For each region or pair of regions in our sample,
we give a more detailed description of the physical properties
(supplementing section~\ref{sec:regions-milky-way})
together with additional details of the structure function
(supplementing section~\ref{sec:results})
and comparison with previous results from the literature
(supplementing section~\ref{sec:comp-with-prev}).

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
In this case we merge the first three points of the structure function.
A detailed description of the model fit is given in
section~\ref{sec:example-results-orion} and will
not be repeated here.
At the largest scales, which are not used in the model fitting,
one sees a downturn in the structure function from
\SI{22}{km^{2}.s^{-2}} for \(r < \SI{0.3}{pc}\) to
\SI{7}{km^{2}.s^{-2}} at \(r = \SI{0.5}{pc}\)
(open symbols in Figure~\ref{fig:strucfunc-fit-Galactic}a).
This is similar to the behavior expected for tapered fluctuations
(see section~\ref{sec:limit-model-struct} and Figure~\ref{fig:model-strucfunc}b)
in which the velocity dispersion is higher in the center of the map
than in the periphery.

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
They observed a tendency that higher ionization lines presents higher  dispersion and the steepness of the structure function slope. 
Their results just consider one Gaussian component. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.

>>>>

\subsection{Comparison with previous structure functions}

Comparison with prior studies is complicated by the
diversity of methodologies that  have been employed.
There is almost universal agreement on how to measure
the velocity variance \(\sigma^2\pos\),
although even here there can be small differences according
to whether the centroid velocities come from gaussian fitting
or velocity moments,
and whether or not smooth large-scale trends are first removed.
\citet{arthur2016turbulence} compared multiple studies of the
inner Orion Nebula, finding agreement to within 20\%
in \(\sigma^2\pos\) determinations
for emission lines that trace the bulk of the fully ionized gas.

@@

\section{\boldmath Notes on individual \hii{} regions}
\label{sec:notes-individual-hii}
For each region or pair of regions in our sample,
we give a more description of its physical properties
(supplementing section~\ref{sec:regions-milky-way})
together with additional details of the structure function
(supplementing section~\ref{sec:results}).

@@

Figure~\ref{fig:strucfunc-fit-Galactic}a shows the structure function of the Orion core.
In this case we merge the first three points of the structure function.
%From \SI{0.002}{pc} until \SI{0.003}{pc} all points fall below the true model showing that they are affected by the seeing. 
%The correlation length for the Orion core is \SI{0.07}{pc}, it has a \(\sigma^2\pos\) of \SI{12}{km^{2}.s^{-2}} and an index of \num{1.07}.
The structure function of the Orion core behaves accordingly to the tapered case of inhomogeneous fluctuations (see Figure~\ref{fig:model-strucfunc}b).
At \SI{0.25}{pc} there is a plateau around \SI{22}{km^{2}.s^{-2}}.
Above separations of \SI{0.3}{pc} the structure function decays to a value of \SI{7}{km^{2}.s^{-2}} at  \SI{0.5}{pc}.

@@

\citet{arthur2016turbulence} carried out a complete analysis by calculating the structure function of different emission lines in the inner Orion Nebula.
They observed a tendency that higher ionization lines presents higher values on the magnitude dispersion and the steepness of the structure function slope. 
Their results just consider one Gaussian component. 
The power-law index obtained by \citet{arthur2016turbulence} are \(m \sim 1.2 \pm 0.1\) for \halpha\ and [OIII] emission lines and for [SII] they found \(m \sim 0.8 \pm 0.1\). 
The correlation length for all lines is \SI{\approx 0.05}{pc}, value obtained when the structure function is equal to \(\sigma\pos^2\).
For the same \halpha\ observation we obtained a value of \num{1.07} and a correlation length of \SI{0.068}{pc}. 
Although the work of \citet{arthur2016turbulence} follows a different methodology, the values of \(r_0\) and \(\sigma\pos^2\) fall within the margin error.
